Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
explain CEK

\citet{siek2009exploring} present another intermediate langauge for gradually 
typed language, cast calculus \castCalculus\ and achieve both blame-tracking 
and space-efficiency for this language by decorating \citet{herman2010space}'s 
coercions with labels. \castCalculus\ is simply typed lambda calculus extended 
with the dynamic type and cast expressions. The labels in \castCalculus\, 
unlike their counterparts in the Blame Calculus, have no polarity. 
They also propose that there are four blame strategies for \castCalculus{}:
$ \{Lazy, Eager\} \times \{D, UD\} $. Eager strategies detect more potential 
type errors, but blame more programs. $ D $ and $ UD $ assign blame labels 
differently. They claim that their \lazyUD\ cast calculus is the same as the 
Blame Calculus, modulo label polarity, and prove that their their \lazyUD\ 
coercion calculus simulates their \lazyUD{} cast calculus. It is unknown, 
however, whether the simulation in the other direction also works.
\todo[inline]{Is it important to this paper whether there is a
simulation in the other direction? -Jeremy
\\ --- \\
I guessed to say coercion is correct the other direction is 
necessary. -KC}

@@

	\stxrule{\kappa}{continuations}{
		\mathtt{stop} \mid{}
		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{cons_2} \; v \; \kappa \mid{}
		\mathtt{inl} \; \kappa \mid{}
		\mathtt{inr} \; \kappa
	}
	\stxrulecont{
		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{app_2} \; v \; \kappa \mid{}
		\mathtt{fst} \; \kappa \mid{}
		\mathtt{snd} \; \kappa \mid
		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa
	}
	\stxrulecont{	
		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa \mid
		\langle c \rangle \kappa
	}
	\end{array}
	\]
	Syntax
	\[
	\begin{array}{rclr}
	\stxrule{r}{cast results}{
		\rOOsucc{v} \mid
		\rOOfail{l}
	}
	\stxrule{s}{states}{
		\sOOinspect{e}{\rho}{\kappa} \mid{}
		\sOOreturn{v}{\kappa} \mid{}
		\sOOhalt{o}
	}

@@

Fig.~\ref{machine-cekc} defines the dynamic semantics of cast calculi as a 
CEK machine \citep{felleisen1986control}.
\todo[inline]{Briefly present the main ideas regarding how a CEK
	machine works. (2-3 sentences) -Jeremy}
\todo[inline]{Please fill in the missing reduction rules. -Jeremy}
\todo[inline]{Explain why you are using a CEK machine instead of
	reduction semantics. -Jeremy}
\todo[inline]{Change the order of parameters for applyCast to take
	the value first and the cast second. -Jeremy
	\\---\\
	Could you tell me why taking the value first is better?
	I am always taking the target of induction/match first. -KC}

>>>>

\citet{siek2009exploring} present another intermediate langauge for gradually 
typed language, cast calculus \castCalculus\ and achieve both blame-tracking 
and space-efficiency for this language by decorating \citet{herman2010space}'s 
coercions with labels. \castCalculus\ is simply typed lambda calculus extended 
with the dynamic type and cast expressions. The labels in \castCalculus{}, 
unlike their counterparts in the Blame Calculus, have no polarity. 
They also propose that there are four blame strategies for \castCalculus{}:
$ \{Lazy, Eager\} \times \{D, UD\} $. Eager strategies detect more potential 
type errors, but blame more programs. $ D $ and $ UD $ assign blame labels 
differently. They claim that their \lazyUD\ cast calculus is the same as the 
Blame Calculus, modulo label polarity, and prove that their their \lazyUD\ 
coercion calculus simulates their \lazyUD{} cast calculus. It is unknown, 
however, whether the simulation in the other direction also works.
\todo[inline]{Is it important to this paper whether there is a
simulation in the other direction? -Jeremy
\\ --- \\
I guessed to say coercion is correct the other direction is 
necessary. -KC}

@@

@@

Fig.~\ref{machine-cekc} defines the dynamic semantics of cast calculi as a 
CEK machine \citep{felleisen1986control}. CEK machines include continuation as 
part of their states. They evaluate expressions with two interleaving 
processes: 
(1) dive into an expression and extend the continuation;
(2) return a value to the current continuation.
\todo[inline]{Briefly present the main ideas regarding how a CEK
	machine works. (2-3 sentences) -Jeremy
\\---\\Fixed -KC}

Most existing proofs about cast calculi defines the dynamic semantics with 
reduction semantics. We use a CEK machine instead because one of us is more 
familiar with CEK machines, and that he believes CEK machines are more 
convenient because space-efficiency is about compressing continuations.
\todo[inline]{Explain why you are using a CEK machine instead of
	reduction semantics. -Jeremy
\\---\\Fixed -KC}

\todo[inline]{Please fill in the missing reduction rules. -Jeremy}
\todo[inline]{Change the order of parameters for applyCast to take
	the value first and the cast second. -Jeremy
	\\---\\
	Could you tell me why taking the value first is better?
	I am always taking the target of induction first. -KC}
